SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-24 scipy-1.0/paper.tex
"core development team" -> "current core development team" Trying to explain the disconnect between the substantial use of Fortran and C in existing SciPy code and our order of language preference.
Additional modifications to explain difference between language preferences and historical use

For implementing new functionality, Python is the first choice. If Python performance is an issue, then 
we use Cython, C, C++, or Fortran (listed in order of preference). The main motivation for this is
maintainability: Cython has the highest abstraction level and most Python
developers will understand it. C is also widely known, and easier to deal with
for the core development team than C++ and especially Fortran.

While it is not surprising that Python is heavily used in SciPy, the usage
distribution of the other languages warrants some discussion. Fortran is an
extremely well-established scientific programming language, both for historical
reasons and because of its continued excellent
performance\cite{Koelbel:1993:HPF:562354}. We wrap the FFTPACK Fortran library
for performing Fourier transforms\cite{SWARZTRAUBER198445, SWARZTRAUBER198251}
since this library has been a standard in the field for 33 years and has a
license that is compatible with our own. Likewise, we wrap the Fortran source
for ODEPACK\cite{citeulike:2644528} as it has been  trusted for the initial
value problem for ordinary differential equation systems for 30 years. For
similar reasons we also wrap the Fortran libraries
QUADPACK\cite{1983qspa.book.....P} (for numerical integration of
one-dimensional functions), FITPACK\cite{Dierckx:1993:CSF:151103}
(curve-fitting / interpolation), ODRPACK\cite{ODRPACK_Boggs} (orthogonal
distance regression), MINPACK\cite{osti_6997568} (minimization of linear and
nonlinear equations), ARPACK\cite{leh:sor:yan96} (solving large scale
eigenvalue problems), ALGORITHM 644\cite{Amos:1986:APP:7921.214331} (handling
Bessel Functions), and CDFLIB\cite{CDFLIB_site} (evaluation of cumulative
density functions).

>>>>

For implementing \emph{new} functionality, Python is the language of choice. If Python 
performance is an issue, then we use Cython, C, C++, or Fortran (listed in order 
of preference). The main motivation for this is maintainability: Cython has the 
highest abstraction level and most Python developers will understand it. C is 
also widely known, and easier to deal with for the current core development team 
than C++ and especially Fortran. While it is not surprising that Python is heavily 
used in SciPy, the usage distribution of the other languages \textemdash despite 
our preferences for implementing new functionality \textemdash warrants discussion.

Fortran is an
extremely well-established scientific programming language, both for historical
reasons and because of its continued excellent
performance\cite{Koelbel:1993:HPF:562354}. We wrap the FFTPACK Fortran library
for performing Fourier transforms\cite{SWARZTRAUBER198445, SWARZTRAUBER198251}
since this library has been a standard in the field for 33 years and has a
license that is compatible with our own. Likewise, we wrap the Fortran source
for ODEPACK\cite{citeulike:2644528} as it has been  trusted for the initial
value problem for ordinary differential equation systems for 30 years. For
similar reasons we also wrap the Fortran libraries
QUADPACK\cite{1983qspa.book.....P} (for numerical integration of
one-dimensional functions), FITPACK\cite{Dierckx:1993:CSF:151103}
(curve-fitting / interpolation), ODRPACK\cite{ODRPACK_Boggs} (orthogonal
distance regression), MINPACK\cite{osti_6997568} (minimization of linear and
nonlinear equations), ARPACK\cite{leh:sor:yan96} (solving large scale
eigenvalue problems), ALGORITHM 644\cite{Amos:1986:APP:7921.214331} (handling
Bessel Functions), and CDFLIB\cite{CDFLIB_site} (evaluation of cumulative
density functions).
